### 2018-12-04 Sections/QTCP_protocol_stack.tex
Fixed up fig sizes for 1 col
indexing

\begin{figure}[!htbp]\index{QTCP protocol stack}
\includegraphics[clip=true, width=0.475\textwidth]{stack}
\captionspacefig \caption{Protocol stack for QTCP. The protocol stack mediates communication of quantum data from Alice to Bob using the shown layers of abstraction. The end goal is to provide Bob a virtual interface to Alice's transmitted data, while remaining oblivious to the underlying protocol.} \label{fig:stack}\index{QTCP protocol stack}
\end{figure}

@@

As an alternative to checksums, we could borrow the notion of quantum error correction (QEC)\index{Quantum error correction (QEC)} and fault-tolerance\index{Fault-tolerance} from quantum computing theory \cite{???}. Here we encode a quantum state into a (polynomially) larger Hilbert space. \textit{Syndrome measurements}\index{Syndrome!Measurements} on some of the states in this larger space allow us to both detect and correct universal error models, such as depolarisation or dephasing, provided that error rates are within the fault-tolerance threshold of the code being employed.

>>>>

\begin{figure}[!htbp]\index{QTCP protocol stack}
\if 2\pubmode
\includegraphics[clip=true, width=0.475\textwidth]{stack}
\else
\includegraphics[clip=true, width=0.6\textwidth]{stack}
\fi
\captionspacefig \caption{Protocol stack for QTCP. The protocol stack mediates communication of quantum data from Alice to Bob using the shown layers of abstraction. The end goal is to provide Bob a virtual interface to Alice's transmitted data, while remaining oblivious to the underlying protocol.} \label{fig:stack}\index{QTCP protocol stack}
\end{figure}

@@

As an alternative to checksums, we could borrow the notion of quantum error correction (QEC)\index{Quantum error correction (QEC)} and fault-tolerance\index{Fault-tolerance} from quantum computing theory \cite{???}. Here we encode a quantum state into a (polynomially) larger Hilbert space. \textit{Syndrome measurements}\index{Syndromes!Measurements} on some of the states in this larger space allow us to both detect and correct universal error models, such as depolarisation or dephasing, provided that error rates are within the fault-tolerance threshold of the code being employed.

### 2018-12-04 Sections/cloud_quantum_computing.tex
Figure resizing. minor.
indexing

The attractive feature of quantum computing is the potentially exponential improvement in algorithmic performance of certain tasks over their classical counterparts as the size of the computer grows. This exponential relationship implies that computation in general no longer has a simple linear tradeoff as the number of participating nodes increases. In Sec.~\ref{sec:comp_sc_func} we quantify this via so-called \textit{computational scaling functions}\index{Computational scaling functions} and study its economic implications in detail.

@@

Perhaps the simplest illustrative example is to consider the execution of a Monte Carlo simulation\index{Monte Carlo simulation}. Here we wish to execute a large number of instances of the same problem, each with a different random seed, and average the results to yield a statistical outcome. Here the \textsc{Map} algorithm simply delegates out $k$ copies of the same algorithm, assigning each node a different random seed\index{Random seed}, and the \textsc{Reduce} algorithm needs only average their outputs. Note that the \textsc{Map} and \textsc{Reduce} algorithms are relatively simple, with the nodes operating in parallel doing all the hardcore number crunching.

@@

\begin{figure}[!htb]
	\includegraphics[clip=true, width=0.475\textwidth]{error_averaging_map_reduce}
	\captionspacefig \caption{Representing the unitary error averaging technique for error-correcting passive linear optics in parallelised form, consistent with the \textsc{Quantum MapReduce} structure.}\label{fig:error_av_map_reduce}
\end{figure}

@@

\subsection{Delegated quantum computation} 
\index{Delegated quantum computation}

@@

We anticipate that some of the first experiments will be extensions of what are already performed on Earth. For example, one can perform increasingly long space-based Bell violation tests\index{Bell inequality} at unprecedented distances \cite{bib:yin2017satellite}. Another possibility is to examine the speed of influence of entanglement \cite{bib:yin2013lower}. In space, such experiments could be extended much further, giving tighter bounds. There are demanding technical hurdles that must be overcome to succeed at such experiments, such as the necessity for synchronised clocks (Sec.~\ref{sec:clock_sync}).

@@

The QTCP protocol presented in Sec.~\ref{sec:QTCP} provides an extensible framework for facilitating these kinds of outsourced or delegated protocols\index{Outsourced!Protocols}\index{Delegated protocols} using generic quantum assets. Bear in mind that, as designed, the payload of QTCP packets could encapsulate all manner of optical states, or mediate long-distance interaction between them.

>>>>

The attractive feature of quantum computing is the potentially exponential improvement in algorithmic performance of certain tasks over their classical counterparts as the size of the computer grows. This exponential relationship implies that computation in general no longer has a simple linear tradeoff as the number of participating nodes increases. In Sec.~\ref{sec:comp_sc_func} we quantify this via so-called \textit{computational scaling functions}\index{Computational!Scaling functions} and study its economic implications in detail.

@@

Perhaps the simplest illustrative example is to consider the execution of a Monte Carlo simulation\index{Monte-Carlo simulations}. Here we wish to execute a large number of instances of the same problem, each with a different random seed, and average the results to yield a statistical outcome. Here the \textsc{Map} algorithm simply delegates out $k$ copies of the same algorithm, assigning each node a different random seed\index{Random seed}, and the \textsc{Reduce} algorithm needs only average their outputs. Note that the \textsc{Map} and \textsc{Reduce} algorithms are relatively simple, with the nodes operating in parallel doing all the hardcore number crunching.

@@

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{error_averaging_map_reduce}
	\captionspacefig \caption{Representing the unitary error averaging technique for error-correcting passive linear optics in parallelised form, consistent with the \textsc{Quantum MapReduce} structure.}\label{fig:error_av_map_reduce}
\end{figure}

@@

\subsection{Delegated quantum computation} 
\index{Delegated!Quantum computation}

@@

We anticipate that some of the first experiments will be extensions of what are already performed on Earth. For example, one can perform increasingly long space-based Bell violation tests\index{Bell!Inequality} at unprecedented distances \cite{bib:yin2017satellite}. Another possibility is to examine the speed of influence of entanglement \cite{bib:yin2013lower}. In space, such experiments could be extended much further, giving tighter bounds. There are demanding technical hurdles that must be overcome to succeed at such experiments, such as the necessity for synchronised clocks (Sec.~\ref{sec:clock_sync}).

@@

The QTCP protocol presented in Sec.~\ref{sec:QTCP} provides an extensible framework for facilitating these kinds of outsourced or delegated protocols\index{Outsourced!Protocols}\index{Delegated!Protocols} using generic quantum assets. Bear in mind that, as designed, the payload of QTCP packets could encapsulate all manner of optical states, or mediate long-distance interaction between them.

### 2018-12-04 Sections/costs_and_attributes_in_quantum_networks.tex
More indexing
Finished indexing hierarchy
braket
indexing

\subsubsection{Efficiency} \index{Loss channel}

@@

\subsubsection{Spectral filtering} \index{Loss channel}\index{Spectral filtering}

@@

\subsubsection{Decoherence} \index{Dephasing channel} \index{Depolarising channel} \index{Decoherence}

@@

The fidelity\index{Fidelity} between two states is defined as,
\begin{align}
\mathcal{F}(\hat\rho_1,\hat\rho_2) = \mathrm{tr}\left(\sqrt{\hat\rho_1^{1/2}\cdot\hat\rho_2\cdot\hat\rho_1^{1/2}}\right),
\end{align}
where,
\begin{align}
& \mathcal{F}(\hat\rho_1,\hat\rho_2) = \mathcal{F}(\hat\rho_2,\hat\rho_1), \nonumber \\
& 0\leq \mathcal{F}(\hat\rho_1,\hat\rho_2) \leq 1.
\end{align}
\mbox{$\mathcal{F}(\hat\rho_1,\hat\rho_2)=1$} iff the states are equal, and \mbox{$\mathcal{F}(\hat\rho_1,\hat\rho_2)=0$} iff they are orthogonal.
In the case where one of the states is a pure state, this simplifies to,
\begin{align}
\mathcal{F}(\hat\rho_1,\ket{\psi_2}) = \bra{\psi_2}\hat\rho_1\ket{\psi_2},
\end{align}
and when both states are pure to simply,
\begin{align}
\mathcal{F}(\ket{\psi_1},\ket{\psi_2}) = |\langle\psi_1 | \psi_2\rangle|^2.
\end{align}

@@

\subsubsection{Phase-space} \index{Phase-space errors}

@@

\subsubsection{Channel capacity} \label{sec:channel_cap} \index{Channel capacity}

The measures considered until now have quantified the preservation of quantum states. Alternately, one might consider information theoretic measures, which quantify the number of bits/qubits transmitted by a link, i.e the number of bits/qubits in common before and after the channel. This is an extremely powerful tool as it upper bounds the amount of information the receiver can extract from the transmitter under \textit{any} measurement scheme, very useful in a cryptographic context, where we want security to be attack-independent\index{Information-theoretic security} (Sec.~\ref{sec:comp_vs_inf_th_sec}).

@@

The mutual information is defined as being between a particular known pair of states. Of course, in a quantum network we will seldom know what the states being communicated are and will therefore be unable to directly calculate the mutual information. To address this, the \textit{classical channel capacity}\index{Classical channel capacity} of a channel is defined as,
\begin{align}\index{Channel capacity}
\mathcal{C}(\mathcal{E}) = \max_{\hat\rho} [I(\hat\rho,\mathcal{E}(\hat\rho))],
\end{align}
with the intuitive interpretation as the maximum mutual information between input and output states that can be achieved for the channel. (Note: this definition of `capacity' is not to be confused with that which we later refer to in flow networks).

@@

The quantum coherent information exhibits much of the same mathematical structure as the classical mutual information. And analogously, we can define the \textit{quantum channel capacity} as,
\begin{align}\index{Quantum channel capacity}
\mathcal{Q}(\mathcal{E}) = \max_{\hat\rho} I(\hat\rho,\mathcal{E}).
\end{align}

>>>>

\subsubsection{Efficiency} \index{Loss!Channel}

@@

\subsubsection{Spectral filtering} \index{Loss!Channel}\index{Spectral filtering}

@@

\subsubsection{Decoherence} \index{Dephasing!Channel} \index{Depolarising channel} \index{Decoherence}

@@

The fidelity\index{Fidelity} between two states is defined as,
\begin{align}
\mathcal{F}(\hat\rho_1,\hat\rho_2) = \mathrm{tr}\left(\sqrt{\hat\rho_1^{1/2}\cdot\hat\rho_2\cdot\hat\rho_1^{1/2}}\right),
\end{align}
where,
\begin{align}
& \mathcal{F}(\hat\rho_1,\hat\rho_2) = \mathcal{F}(\hat\rho_2,\hat\rho_1), \nonumber \\
& 0\leq \mathcal{F}(\hat\rho_1,\hat\rho_2) \leq 1.
\end{align}
\mbox{$\mathcal{F}(\hat\rho_1,\hat\rho_2)=1$} iff the states are equal, and \mbox{$\mathcal{F}(\hat\rho_1,\hat\rho_2)=0$} iff they are orthogonal.
In the case where one of the states is a pure state, this simplifies to,
\begin{align}
\mathcal{F}(\hat\rho_1,\ket{\psi_2}) = \bra{\psi_2}\hat\rho_1\ket{\psi_2},
\end{align}
and when both states are pure to simply,
\begin{align}
\mathcal{F}(\ket{\psi_1},\ket{\psi_2}) = |\braket{\psi_1 | \psi_2}|^2.
\end{align}

@@

\subsubsection{Phase-space} \index{Phase-space!Errors}

@@

\subsubsection{Channel capacity} \label{sec:channel_cap} \index{Channels!Capacity}

The measures considered until now have quantified the preservation of quantum states. Alternately, one might consider information theoretic measures, which quantify the number of bits/qubits transmitted by a link, i.e the number of bits/qubits in common before and after the channel. This is an extremely powerful tool as it upper bounds the amount of information the receiver can extract from the transmitter under \textit{any} measurement scheme, very useful in a cryptographic context, where we want security to be attack-independent\index{Information-theoretic!Security} (Sec.~\ref{sec:comp_vs_inf_th_sec}).

@@

The mutual information is defined as being between a particular known pair of states. Of course, in a quantum network we will seldom know what the states being communicated are and will therefore be unable to directly calculate the mutual information. To address this, the \textit{classical channel capacity}\index{Classical channel capacity} of a channel is defined as,
\begin{align}\index{Channels!Capacity}
\mathcal{C}(\mathcal{E}) = \max_{\hat\rho} [I(\hat\rho,\mathcal{E}(\hat\rho))],
\end{align}
with the intuitive interpretation as the maximum mutual information between input and output states that can be achieved for the channel. (Note: this definition of `capacity' is not to be confused with that which we later refer to in flow networks).

@@

The quantum coherent information exhibits much of the same mathematical structure as the classical mutual information. And analogously, we can define the \textit{quantum channel capacity} as,
\begin{align}\index{Quantum channels!Capacity}
\mathcal{Q}(\mathcal{E}) = \max_{\hat\rho} I(\hat\rho,\mathcal{E}).
\end{align}

### 2018-12-04 Sections/cryptowars.tex
indexing

\section{What is security?}\index{Computational security}\index{Information-theoretic security}\label{sec:comp_vs_inf_th_sec}

\dropcap{B}{efore} describing any specific cryptographic protocols, let us define what is meant by `security' in a cryptographic context. We differentiate between \textit{information theoretic security}\index{Information-theoretic security}, as opposed to \textit{computational security}\index{Computational security}:

@@

There is one and only one \textit{provably} secure (in the sense of information-theoretic security\index{Information-theoretic security} as opposed to computational security\index{Computational security}) encryption protocol -- the \textit{one-time pad}\index{One-time pad}. This protocol requires Alice and Bob to share a random secret-key as long as the message (plaintext\index{Plaintext}) being communicated between them. The two bit-strings undergo bit-wise XOR operations to form the ciphertext\index{Ciphertext}. Mathematically,\index{One-time pad}
\begin{align}
c = s \oplus k,
\end{align}
where $\oplus$ is the bitwise XOR operation (equivalently addition modulo 2), and $c$, $s$ and $k$ are the ciphertext, plaintext and key bit-strings respectively, all of which are of the same length,
\begin{align}
	|c|=|s|=|k|.
\end{align}

The security of this protocol is easy to see intuitively -- with an appropriate choice of key, \textit{any} plaintext of the same length could be inferred from \textit{any} ciphertext. This means that there is no possibility of performing any kind of frequency analysis\index{Frequency analysis}, as the ciphertext string has maximum entropy\index{Entropy} (inherited from the maximum entropy of the random key, and assuming a strong cryptographic random bit generator) and thus no correlations. Since every possible valid plaintext can be recovered using an appropriate key, a cracking algorithm is unable to find a unique plaintext matching the ciphertext, since all are equally valid decryptions.

Importantly, the secrecy of the one-time pad\index{One-time pad} strictly requires that a key never be reused. A fresh key must be generated for each message sent, otherwise trivial frequency analysis\index{Frequency analysis} techniques can be employed to compromise security. If the same key $k$ is used to encode two messages $s_1$ and $s_2$, yielding ciphertexts,
\begin{align}
c_1&=s_1\oplus k,\nonumber\\
c_2&=s_2\oplus k,
\end{align}
then we trivially obtain,
\begin{align}
c_1 \oplus c_2 &= (s_1 \oplus k) \oplus (s_2 \oplus k) \nonumber \\
&= (s_1 \oplus s_2) \oplus (k \oplus k) \nonumber \\
&= s_1 \oplus s_2,
\end{align}
which is independent of the key. Now a frequency analysis on the bitwise XOR of two plaintexts can be applied, without requiring any knowledge of the key whatsoever.

@@

\section{Attacks on classical cryptography}\index{Cryptographic attacks}\label{sec:attacks_on_class}

@@

Thankfully, there are two saving graces. First of all, much research is being carried out into \textit{post-quantum classical cryptography}\index{Post-quantum classical cryptography}. That is, public-key cryptosystems based upon trapdoor functions\index{One-way functions} that reside outside of \textbf{BQP} and are therefore not efficiently attacked by quantum computers. One such line of research is to construct cryptosystems based upon \textbf{NP}-complete problems, such as the McEliece protocol\index{McEliece protocol} \cite{bib:McEliece}. Recall from Fig.~\ref{fig:complexity_classes} that \textbf{NP}-complete is strongly believed to reside completely outside of \textbf{BQP}. However, while many computer scientists might be comfortable with such a level of security, it is nonetheless based on the unproven conjecture that \textbf{NP}-complete and \textbf{BQP} do not intersect, i.e \mbox{$\mathbf{NP}\nsubseteq\mathbf{BQP}$}. What would be much more satisfying would be protocols demonstrating information-theoretic security\index{Information-theoretic security} rather than computational security\index{Computational security}. Here quantum mechanics can help us -- \textit{quantum cryptography}.

@@

Aside from quantum computing, a central use for quantum technologies is in cryptography \cite{bib:Gisin02}. The demand for secure cryptography is now extremely important in the context of electronic commerce and general security of information transmission in the internet age. Electronic currencies such as Bitcoin\index{Bitcoin} depend on cryptographic protocols in order to secure the value of assets, assign ownership certificates\index{Ownership certificates}, and secure the currency against fraud. However, such protocols are based upon the computational complexity of certain mathematical problems (i.e computational security\index{Computational security}), and are not fundamentally secure in the presence of limitless computational resources, or quantum computers. Therefore, using quantum mechanical protocols based on physical principles (i.e information-theoretic security\index{Information-theoretic security}) rather than computational limitations, are favourable for future-proofing ourselves.

Quantum key distribution (QKD) protocols facilitate shared, secret randomness, where any intercept-resend\index{Intercept-resend attacks} (or man-in-the-middle) attack may be detected and rejected, guaranteed by the laws of quantum physics (specifically the Heisenberg uncertainty principle\index{Heisenberg uncertainty principle} and no-cloning theorem\index{No-cloning theorem}). This shared, secret randomness may subsequently be employed in a one-time pad cipher\index{One-time pad}, presenting us with true information-theoretic security\index{Information-theoretic security}.

@@

The BB84 protocol has no measurement timing, mode-matching or interferometric stability requirements, making it a very robust protocol, readily achievable with present-day photonics technology. The scheme has been adapted to physical architectures beyond just polarisation-encoded photons, such as CV encodings\index{Continuous-variables!QKD} \cite{???}.

@@

This is an information-theoretic security\index{Information-theoretic security} result, not a computational security\index{Computational security} one, thereby rescuing the perfect security of the BB84 QKD protocol.

@@

Like BB84, E91 has no mode-matching\index{Mode-matching} or interferometric stability\index{Interferometric stability} requirements, and Alice and Bob both only require single-photon detection. Unlike BB84, however, E91 requires a central authority that is able to prepare entanglement on-demand as a resource.

@@

\subsubsection{Continuous-variable protocols}\index{Continuous-variables!Quantum key distribution}\label{sec:CV_QKD}

@@

Note that this protocol provides information-theoretic security\index{Information-theoretic security}, as per BB84\index{BB84 protocol}, despite the fact that coherent states are non-orthogonal, forming an over-complete basis in phase-space\index{Phase-space}.

@@

Importantly, unlike classical cryptographic protocols, QKD makes no assumptions about the computational complexity of inverting encoding algorithms or trapdoor functions\index{Trapdoor functions}. The protocols are information-theoretically secure\index{Information-theoretic security}, and therefore no physically realisable computer, even a quantum computer, can compromise them. Thus, usual cryptanalytic techniques, like linear and differential cryptanalysis \cite{bib:Schneier96}\index{Linear cryptanalysis}\index{Differential cryptanalysis}, or the ability to factor large numbers\index{Integer factorisation}, that are employed to attack other encryption protocols, do not compromise QKD.

@@

Note that the security of the scheme is information-theoretic\index{Information-theoretic security}, and does not make any assumptions about computational security\index{Computational security}. Thus, this represents a strong form of quantum private-key cryptography, requiring only very short keys compared to message length that may be reused.

However, the scheme is very challenging to implement on a large scale over long distances. Consider an optical implementation, where the message is photonically encoded. Now the scheme represents a complex, multi-mode, generalised Mach-Zehnder interferometer\index{Mach-Zehnder (MZ) interference}, meaning that the channel between Alice and Bob, who might be far apart, must be interferometrically stabilised\index{Interferometric stability} (Sec.~\ref{sec:opt_stab}) on the order of the photons' wavelength (hundreds of nanometers for optical frequencies), which is extremely challenging over long distances.

@@

\dropcap{F}{or} a QKD system, information-theoretic security\index{Information-theoretic security} is achieved only when security against collective, coherent attacks is proven. We mustn't make assumptions about the limitations of our adversaries.

@@

\subsection{Detector attacks}\index{Detector attacks}

>>>>

\section{What is security?}\index{Computational!Security}\index{Information-theoretic!Security}\label{sec:comp_vs_inf_th_sec}

\dropcap{B}{efore} describing any specific cryptographic protocols, let us define what is meant by `security' in a cryptographic context. We differentiate between \textit{information theoretic security}\index{Information-theoretic!Security}, as opposed to \textit{computational security}\index{Computational!Security}:

@@

There is one and only one \textit{provably} secure (in the sense of information-theoretic security\index{Information-theoretic!Security} as opposed to computational security\index{Computational!Security}) encryption protocol -- the \textit{one-time pad}\index{One-time pad}. This protocol requires Alice and Bob to share a random secret-key as long as the message (plaintext\index{Plaintext}) being communicated between them. The two bit-strings undergo bit-wise XOR operations to form the ciphertext\index{Ciphertext}. Mathematically,\index{One-time pad}
\begin{align}
c = s \oplus k,
\end{align}
where $\oplus$ is the bitwise XOR operation (equivalently addition modulo 2), and $c$, $s$ and $k$ are the ciphertext, plaintext and key bit-strings respectively, all of which are of the same length,
\begin{align}
	|c|=|s|=|k|.
\end{align}

The security of this protocol is easy to see intuitively -- with an appropriate choice of key, \textit{any} plaintext of the same length could be inferred from \textit{any} ciphertext. This means that there is no possibility of performing any kind of frequency analysis\index{Frequency!Analysis}, as the ciphertext string has maximum entropy\index{Entropy} (inherited from the maximum entropy of the random key, and assuming a strong cryptographic random bit generator) and thus no correlations. Since every possible valid plaintext can be recovered using an appropriate key, a cracking algorithm is unable to find a unique plaintext matching the ciphertext, since all are equally valid decryptions.

Importantly, the secrecy of the one-time pad\index{One-time pad} strictly requires that a key never be reused. A fresh key must be generated for each message sent, otherwise trivial frequency analysis\index{Frequency!Analysis} techniques can be employed to compromise security. If the same key $k$ is used to encode two messages $s_1$ and $s_2$, yielding ciphertexts,
\begin{align}
c_1&=s_1\oplus k,\nonumber\\
c_2&=s_2\oplus k,
\end{align}
then we trivially obtain,
\begin{align}
c_1 \oplus c_2 &= (s_1 \oplus k) \oplus (s_2 \oplus k) \nonumber \\
&= (s_1 \oplus s_2) \oplus (k \oplus k) \nonumber \\
&= s_1 \oplus s_2,
\end{align}
which is independent of the key. Now a frequency analysis on the bitwise XOR of two plaintexts can be applied, without requiring any knowledge of the key whatsoever.

@@

\section{Attacks on classical cryptography}\index{Cryptographic!Attacks}\label{sec:attacks_on_class}

@@

Thankfully, there are two saving graces. First of all, much research is being carried out into \textit{post-quantum classical cryptography}\index{Post-quantum classical cryptography}. That is, public-key cryptosystems based upon trapdoor functions\index{One-way functions} that reside outside of \textbf{BQP} and are therefore not efficiently attacked by quantum computers. One such line of research is to construct cryptosystems based upon \textbf{NP}-complete problems, such as the McEliece protocol\index{McEliece protocol} \cite{bib:McEliece}. Recall from Fig.~\ref{fig:complexity_classes} that \textbf{NP}-complete is strongly believed to reside completely outside of \textbf{BQP}. However, while many computer scientists might be comfortable with such a level of security, it is nonetheless based on the unproven conjecture that \textbf{NP}-complete and \textbf{BQP} do not intersect, i.e \mbox{$\mathbf{NP}\nsubseteq\mathbf{BQP}$}. What would be much more satisfying would be protocols demonstrating information-theoretic security\index{Information-theoretic!Security} rather than computational security\index{Computational!Security}. Here quantum mechanics can help us -- \textit{quantum cryptography}.

@@

Aside from quantum computing, a central use for quantum technologies is in cryptography \cite{bib:Gisin02}. The demand for secure cryptography is now extremely important in the context of electronic commerce and general security of information transmission in the internet age. Electronic currencies such as Bitcoin\index{Bitcoin} depend on cryptographic protocols in order to secure the value of assets, assign ownership certificates\index{Ownership certificates}, and secure the currency against fraud. However, such protocols are based upon the computational complexity of certain mathematical problems (i.e computational security\index{Computational!Security}), and are not fundamentally secure in the presence of limitless computational resources, or quantum computers. Therefore, using quantum mechanical protocols based on physical principles (i.e information-theoretic security\index{Information-theoretic!Security}) rather than computational limitations, are favourable for future-proofing ourselves.

Quantum key distribution (QKD) protocols facilitate shared, secret randomness, where any intercept-resend\index{Intercept-resend attacks} (or man-in-the-middle) attack may be detected and rejected, guaranteed by the laws of quantum physics (specifically the Heisenberg uncertainty principle\index{Heisenberg!Uncertainty principle} and no-cloning theorem\index{No-cloning theorem}). This shared, secret randomness may subsequently be employed in a one-time pad cipher\index{One-time pad}, presenting us with true information-theoretic security\index{Information-theoretic!Security}.

@@

The BB84 protocol has no measurement timing, mode-matching or interferometric stability requirements, making it a very robust protocol, readily achievable with present-day photonics technology. The scheme has been adapted to physical architectures beyond just polarisation-encoded photons, such as CV encodings\index{Continuous-variables!Quantum key distribution (QKD)} \cite{???}.

@@

This is an information-theoretic security\index{Information-theoretic!Security} result, not a computational security\index{Computational!Security} one, thereby rescuing the perfect security of the BB84 QKD protocol.

@@

Like BB84, E91 has no mode-matching\index{Mode-matching} or interferometric stability\index{Interferometric!Stability} requirements, and Alice and Bob both only require single-photon detection. Unlike BB84, however, E91 requires a central authority that is able to prepare entanglement on-demand as a resource.

@@

\subsubsection{Continuous-variable protocols}\index{Continuous-variables!Quantum key distribution (QKD)}\label{sec:CV_QKD}

@@

Note that this protocol provides information-theoretic security\index{Information-theoretic!Security}, as per BB84\index{BB84 protocol}, despite the fact that coherent states are non-orthogonal, forming an over-complete basis in phase-space\index{Phase-space}.

@@

Importantly, unlike classical cryptographic protocols, QKD makes no assumptions about the computational complexity of inverting encoding algorithms or trapdoor functions\index{Trapdoor functions}. The protocols are information-theoretically secure\index{Information-theoretic!Security}, and therefore no physically realisable computer, even a quantum computer, can compromise them. Thus, usual cryptanalytic techniques, like linear and differential cryptanalysis \cite{bib:Schneier96}\index{Linear cryptanalysis}\index{Differential cryptanalysis}, or the ability to factor large numbers\index{Integer factorisation}, that are employed to attack other encryption protocols, do not compromise QKD.

@@

Note that the security of the scheme is information-theoretic\index{Information-theoretic!Security}, and does not make any assumptions about computational security\index{Computational!Security}. Thus, this represents a strong form of quantum private-key cryptography, requiring only very short keys compared to message length that may be reused.

However, the scheme is very challenging to implement on a large scale over long distances. Consider an optical implementation, where the message is photonically encoded. Now the scheme represents a complex, multi-mode, generalised Mach-Zehnder interferometer\index{Mach-Zehnder (MZ) interference}, meaning that the channel between Alice and Bob, who might be far apart, must be interferometrically stabilised\index{Interferometric!Stability} (Sec.~\ref{sec:opt_stab}) on the order of the photons' wavelength (hundreds of nanometers for optical frequencies), which is extremely challenging over long distances.

@@

\dropcap{F}{or} a QKD system, information-theoretic security\index{Information-theoretic!Security} is achieved only when security against collective, coherent attacks is proven. We mustn't make assumptions about the limitations of our adversaries.

@@

\subsection{Detector attacks}\index{Detector!Attacks}
